---
title: "Oscars 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Oscars 2020 Predictions

Killing time until the Ceremony kicks into full-gear by trying to predict its outcome. 

To be honest, I forgot this was happening in February and therefore ended up scrambling last minute to scrape some data and write the code to do this. As a result, I ended up heavily relying on [another Github user's data](https://github.com/scruwys/and-the-award-goes-to) to train my model. I still had to scrape Wikipedia to complete the dataset, filling the gaps between 2016 and today, which took most of the time I had to do this. Luckily, Oscar prediction models seem to work pretty well using a minimal number of variables.

Hopefully next year I'll be better prepared and can think up of other variables to add to improve my model's accuracy.

### Scraping Pt. 1: Academy Award Nominations, BAFTA, SAG, and GG

The dataset I was using stopped in 2016 so I had to add three years' worth of data. To make my task easier, I decided to scrape Wikipedia. Unfortunately, Wikipedia tables can be pretty messy: the formatting is fairly inconsistent across awards and categories. The links aren't particularly predictable either, so I figure copy-pasting them would save me a bit of time.

Due to this inconsistent formatting, the code below relies on a lot of `if` statements to determine the location of the relevant table. It starts by grabbing the main table with nominations from the URL, and turning it into a table. Some regex tricks are required to retrieve the year. Then, the ordering of Wikipedia tables is used to find the winner (the first entry for every year is typically the winner). The result is cleaned and saved for all links below.

```{r Main Scraping, optionwarning = FALSE, warning=FALSE }
### Loading Libraries ####
library(xml2)
library(httr)
library(rvest)
library(tidyverse)
library(lubridate)
library(caret)

#### Scraping Links ####
## Need to scrape 2016 Onwards
oscar_links <- c(
  "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Actor" = "Actor" ,
  "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Supporting_Actor" = "Supporting Actor",
  "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Supporting_Actress"= "Supporting Actress",
  'https://en.wikipedia.org/wiki/BAFTA_Award_for_Best_Direction' = "Director",
  "https://en.wikipedia.org/wiki/BAFTA_Award_for_Best_Actor" = "Actor",
  "https://en.wikipedia.org/wiki/BAFTA_Award_for_Best_Actress" = "Actress",
  "https://en.wikipedia.org/wiki/BAFTA_Award_for_Best_Supporting_Actor" = "Supporting Actor",
  "https://en.wikipedia.org/wiki/BAFTA_Award_for_Best_Actress_in_a_Supporting_Role" = "Supporting Actress",
  "https://en.wikipedia.org/wiki/BAFTA_Award_for_Best_Adapted_Screenplay" = "Adapted Screenplay",
  "https://en.wikipedia.org/wiki/BAFTA_Award_for_Best_Original_Screenplay" = "Original Screenplay",
  'https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Motion_Picture_%E2%80%93_Drama' = "Best Picture",
  "https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Actor_%E2%80%93_Motion_Picture_Drama" = "Best Picture",
  'https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Director' = "Director",
  "https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Actor_%E2%80%93_Motion_Picture_Drama" = "Actor",
  "https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Actor_%E2%80%93_Motion_Picture_Musical_or_Comedy" = "Actor - Comedy",
  "https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Actress_%E2%80%93_Motion_Picture_Comedy_or_Musical" = "Actress",
  "https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Actress_in_a_Motion_Picture_%E2%80%93_Drama" = "Actress - Drama",
  "https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Supporting_Actress_%E2%80%93_Motion_Picture" = "Supporting Actress",
  "https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Screenplay" = "Adapted Screenplay",
  "https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Screenplay" = "Original Screenplay" ,
  "https://en.wikipedia.org/wiki/Screen_Actors_Guild_Award_for_Outstanding_Performance_by_a_Male_Actor_in_a_Leading_Role" = "Actor",
  "https://en.wikipedia.org/wiki/Screen_Actors_Guild_Award_for_Outstanding_Performance_by_a_Female_Actor_in_a_Leading_Role" = "Actress",
  "https://en.wikipedia.org/wiki/Screen_Actors_Guild_Award_for_Outstanding_Performance_by_a_Male_Actor_in_a_Supporting_Role" = "Supporting Actor",
  "https://en.wikipedia.org/wiki/Screen_Actors_Guild_Award_for_Outstanding_Performance_by_a_Female_Actor_in_a_Supporting_Role" = "Supporting Actress"
)

### Map Get Request ####
get_nominees <- function(award_, link_){

  ## Save Variables
  award_name <- award_
  url <- link_
  
  ## Get HTML Page
  wiki_resp <- read_html(url)
  
  ## Subset Nomination Table
  if (str_detect(url, "Academy_Award") == TRUE){
    num_ <- 2
  } else if (str_detect(url, "BAFTA") == TRUE){
    num_ <- c("Actor" = 8, "Actress" = 7, "Supporting Actor" = 6, "Supporting Actress" = 6,
              "Director" = 6, 
              "Adapted Screenplay" = 4, "Original Screenplay" = 4)[award_name]
  } else if (str_detect(url, "Golden_Globe") == TRUE){
    num_ <- c(
      "Actress" = 7,   "Actress - Drama" = 8, "Supporting Actress" = 8,
      "Director" = 8,  "Best Picture" = 8, "Actor" = 8, "Actor - Comedy" = 7,
      "Adapted Screenplay" = 8, "Original Screenplay" = 8)[award_name]  
  } else {
    num_ <- c("Actress" = 3,   "Actor" = 3, "Supporting Actor" = 3, "Supporting Actress" = 3    )[award_name]
  }
  
  
  wiki_text <- html_table(html_nodes(wiki_resp, ".wikitable"), fill = TRUE)[[num_]] %>%  as.data.frame() 
  
  ## Find Relevant Name (Screenplay Tables are ordered differently)
  if (str_detect(url, "Academy_Awards") == FALSE & str_detect(url, "Screenplay") == TRUE){
    num_ <- 3
  } else{
    num_ <- 2
  }
  
  ## Retrieve & Clean Year, Filter Dataset
  if (str_detect(url, "Academy_Awards") == TRUE){
    
    nominees <- wiki_text %>% 
      select(year = Year, name = names(wiki_text)[2], film = Film) %>% #positional trick so isn't sensitive to actor/actress
      mutate(year = as.numeric(str_extract(year, "[0-9]+"))) %>%
      filter(year > 2016 & year <= 2019)
    
  } else{
    
    if (str_detect(url, "Screenplay|Picture") == TRUE & str_detect(url, "(A|a)ctr.") == FALSE){
      num_ <- 3
    } else{
      num_ <- 2
    }
    
    nominees <- wiki_text %>% 
      select(year = Year, name = names(wiki_text)[num_], film = Film) %>% #positional trick so isn't sensitive to actor/actress
      mutate(year = as.numeric(str_extract(year, "^...."))) %>%
      filter(!is.na(name)) %>%
      filter(year >= 2016 & year <= 2019)
  }
  
  # Select Top Entry For Each Year (is winner)
  ### Note: first() function could be alternative
  winners <- nominees %>%
    split(.$year) %>%
    map(select, name) %>%
    map(head, 1) %>%
    unlist() %>%
    unname()
  
  # Clean Dataset, Add Winner Column, Clean Movie Name
  nominees <- nominees %>%
    mutate(winner = if_else(name %in% winners, 1, 0),
           film = str_replace_all(film, "\\*|†|‡", ""),
           film = str_replace_all(film, "(  )|( $)", ""),
           name = str_replace_all(name, "\\*|†|‡", ""),
           name = str_replace_all(name, "(  )|( $)", ""),
           category = award_name,
           award = str_replace(url, "https://en.wikipedia.org/wiki/", ""),
           award = str_split(award, "_") %>% map(1)
    )
  
  return(nominees)
}

# Run Over All Links, Save as DF
all_nominees <- map2(as.list(oscar_links), as.list(names(oscar_links)), get_nominees) %>%
  do.call("rbind.data.frame", .)

rownames(all_nominees) <- c()

```

Unfortunately, one of the functions I relied on for the code above (`html_table`) failed to work on some Wikipedia tables, due to an inconsistent number of columns within some tables. Without `html_table`, the output came in the form of a vector, alternating between movie name, nominee name, movie name, etc. Quite a bit of subsetting was necessary to move movie names, years, etc, to a separate column.

```{r Scraping More Complicated Links, optionwarning = FALSE, warning=FALSE }
failed_urls <- c("https://en.wikipedia.org/wiki/Golden_Globe_Award_for_Best_Supporting_Actor_%E2%80%93_Motion_Picture", 
                   'https://en.wikipedia.org/wiki/BAFTA_Award_for_Best_Picture',
                   "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Picture",
                   "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Adapted_Screenplay",
                   "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Original_Screenplay",
                   "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Actress")
  
get_failed_links <- function(url){
    
    wiki_resp <- read_html(url)
    
  ## Subset Nomination Table
    if (str_detect(url, "Golden|BAFTA") == TRUE){
      raw_input <- html_nodes(wiki_resp, ".wikitable")[8]
    } else if (str_detect(url, "Academy_Award") == TRUE & str_detect(url, "Original|Actress") == FALSE){
      raw_input <- html_nodes(wiki_resp, ".wikitable")[10]
    }else if (str_detect(url, "Academy_Award") == TRUE & str_detect(url, "Actress") == TRUE){
      raw_input <- html_nodes(wiki_resp, ".wikitable")[2]
    } else{
      raw_input <- html_nodes(wiki_resp, ".wikitable")[8]
    }
    
    ## Finding the Path to Relevant Text 
    raw_input <- raw_input %>% 
      html_nodes("tr") %>% 
      html_nodes("td") %>% 
      html_text() %>%
      str_replace_all("\n{1,}", " ") %>%
      str_replace_all("\\(.{1,}\\)", "") %>% #removing things between (parenthesis)
      str_replace_all("( $)|( {2,})", "") %>% #replacing extra spaces
      str_replace_all("(\\[)|(\\])", "") %>% #removing []
      str_replace_all(" [0-9]$", "")#replacing footnotes
    
    ## Save as DF
    raw_input <- as.data.frame(raw_input, stringsAsFactors = FALSE)
    names(raw_input) <- c("name")
    
    ## Add year As Separate Column
    if (str_detect(url, "Academy_Award_for_Best_Original_Screenplay") == TRUE){
      year_row <- 1 + 10 * c(1:(nrow(raw_input) / 10) - 1) #everyt 10th row
      year_ <- 2010 + c(1:(nrow(raw_input) / 10) - 1) 
      raw_input$year <- NA
      raw_input$year[year_row] <- year_
    } else if(str_detect(url, "Academy_Award_for_Best_Actress") == TRUE){ ## scraping only gets footnote number, converts it to year
      raw_input$year <- as.numeric(raw_input$name) + 1918
      raw_input$name[!is.na(raw_input$year)] <- raw_input$year[!is.na(raw_input$year)]
      raw_input$year <- c(raw_input$year[4:nrow(raw_input)], rep(NA, 3)) ## shift year by 3 bc of weird footnote ordering
    }  else{
      raw_input$year <- as.numeric(raw_input$name)
      raw_input$year[raw_input$year == 1917] <- NA #ignoring 1917, which is a movie
    }
    
    raw_input <- raw_input %>% fill(year) %>% filter(year != name) %>% filter(year >= 2016) %>% filter(name != "Best Film")
    
  ## Remove Character Names
  if ( str_detect(url, "Golden_Globe") == TRUE & str_detect(url, "Supporting") == TRUE ){
    character_name <- 2 + 3 * c(0:nrow(raw_input)) #every third row 
    raw_input <- raw_input[-c(character_name), ]
    rm(character_name)
  } else if ( str_detect(url, "BAFTA") == TRUE){
    character_name <- 3 + 4 * c(0:nrow(raw_input)) #every fourth row 
    raw_input <- raw_input[-c(character_name), ]
    rm(character_name)
  } else if  ( str_detect(url, "Academy_Award") == TRUE & str_detect(url, "Adapted_Screenplay") == TRUE ){
    character_name <-  3 * c(1:(nrow(raw_input) / 3)) #removing name of OG script
    raw_input <- raw_input[-c(character_name), ]
    rm(character_name)
  } else if  ( str_detect(url, "Academy_Award") == TRUE & str_detect(url, "Best_Actress") == TRUE ){
    character_name <-  2 + 3 * c(0:(nrow(raw_input) / 3)) #removing name of OG script
    raw_input <- raw_input[-c(character_name), ]
    rm(character_name)
  }
  
  rownames(raw_input) <- c() #reset rows
  
  # Add Movie Names
  raw_input$film <- NA
  
  if (str_detect(url, "Golden_Globe") == TRUE & str_detect(url, "Supporting")){
    film_name <- 2 * c(1:(nrow(raw_input)/2))
    raw_input$film[film_name - 1] <- raw_input$name[film_name]
  } else if  ( str_detect(url, "BAFTA") == TRUE) {
    film_name <- 1 + 3 * c(0:(nrow(raw_input)/3 - 1))
    raw_input$film[film_name] <- raw_input$name[film_name]
  } else if (str_detect(url, "Academy_Award") == TRUE & ( str_detect(url, "Best_Picture") == TRUE | str_detect(url, "Screenplay") == TRUE ) ) {
    film_name <- 1 + 2 * c(0:(nrow(raw_input)/2 - 1)) #every two rows starting with first row
    raw_input$film[film_name] <- raw_input$name[film_name]
  } else{
    film_name <- 2 * c(1:(nrow(raw_input)/2 ))
    raw_input$film[film_name - 1] <- raw_input$name[film_name]
  }
  
  nominees <- raw_input %>% fill(film) %>% filter(film != name)
  
  ## Removing Country
  if (str_detect(url, "BAFTA_Award_for_Best_Picture") == TRUE){
    country_name <- 2 * c(0:(nrow(raw_input)/2))
    nominees <- nominees[-country_name, ]
  }
  
  ## Adding Winners
  winners <- nominees %>%
    split(.$year) %>%
    map(select, name) %>%
    map(head, 1) %>%
    unlist() %>%
    unname()
  
  ## Cleaning Nominees
  nominees <- nominees %>%
    mutate(winner = if_else(name %in% winners, 1, 0),
           film = str_replace_all(film, "\\*|†|‡", ""),
           film = str_replace_all(film, "(  )|( $)", ""),
           name = str_replace_all(name, "\\*|†|‡", ""),
           name = str_replace_all(name, "(  )|( $)", ""),
           category = url %>% str_split("for_") %>% map(2),
           category = category %>% str_split("%") %>% map(1),
           category = str_replace_all(category, "_", " "),
           award = str_replace(url, "https://en.wikipedia.org/wiki/", ""),
           award = str_split(award, "_") %>% map(1))
  
  return(nominees)
}


other_nominations <- map(as.list(failed_urls), get_failed_links) %>% do.call("rbind.data.frame", .)
```

I was eventually able to scrape everything but the [Academy Award for Best Director]("https://en.wikipedia.org/wiki/Academy_Award_for_Best_Director").

Here are the two dataframes:
```{r Previewing Output}
all_nominees %>% head()
other_nominations %>% head()
```


The next step was to combine the result of both scraping scripts together:
```{r Combining Scraping Output, optionwarning = FALSE, warning=FALSE }
### COMBINING THE NOMINATIONS ####
nominees <- rbind(all_nominees, other_nominations)

nominees <- nominees %>% mutate(
  winner = if_else(year == 2019 & award == "oscar", 0, winner), #setting winner as 0 for all oscars nominees of this year
  category = str_split(category, " -") %>% map(1), #cleaning category
  category = as.character(category),
  category = str_replace_all(category, '(Best )|\\"|( $)', ""),
  award = as.character(award)
  )  %>% 
  mutate(
    award = case_when( #cleaning award names for later
      award == "Golden" ~ "GG",
      award == "Academy" ~ "oscar",
      T ~ award
    )
  ) %>%
  distinct() 

nominees %>% head()
```


### Scraping Pt. 2: Movie-Specific Information

After collecting the names of all Oscar nominees and the results of other award nominations, the next step was to get other relevant bits of information for my predictive model. Based on last year's code, I figured the bare minimum would be to add the movie's release date (simplified into a monthly dummy (e.g., 1 for January, 2 for February, etc)), a run-time variable, a `stars_count` variable (a proxy for star power (and, controversially, movie quality)) and a `writers_count` variable. 

Those variables also had the advantage of having been included and defined in the [afore-mentioned dataset](https://github.com/scruwys/and-the-award-goes-to).

The first step was to find the links of every movie nominated for an Oscar past 2016. The code is slightly different from the previous step: I mainly focus on collecting the `href` attribute for every nominee.

```{r Finding Movie Links, optionwarning = FALSE, warning=FALSE }
### RETRIEVING WIKI LINKS FOR FURTHER INFO ####
oscar_links <- c(
  "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Actor",
  "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Actress",
  "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Supporting_Actor",
  "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Supporting_Actress",
  "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Picture", 
  "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Adapted_Screenplay", 
  "https://en.wikipedia.org/wiki/Academy_Award_for_Best_Original_Screenplay" 
)


### GETTING URLS FOR RECENT MOVIES ####
get_wiki_urls <- function(url){
  
  wiki_resp <- read_html(url)

  ## Get Relevant Table
  if (str_detect(url, "Best_Picture|Screenplay") == TRUE & str_detect(url, "Original") == FALSE){
    raw_input <- html_nodes(wiki_resp, ".wikitable")[10]
  } else if (str_detect(url, "(Actor)|(Actress)") == TRUE){
    raw_input <- html_nodes(wiki_resp, ".wikitable")[2]
  } else{
    raw_input <- html_nodes(wiki_resp, ".wikitable")[8]
  }
  
  ## Get Links
  raw_input <- raw_input %>% 
    html_nodes("tr") %>% 
    html_nodes("td") %>% 
    html_nodes("a") %>% 
    html_attr("href")
  
  raw_input <- as.data.frame(raw_input, stringsAsFactors = FALSE)
  names(raw_input) <- c("link")
  
  ## Cleaning Input
  raw_input <- raw_input %>%
    mutate(
      film = str_replace_all(link, "/wiki/", ""),
      film = str_replace_all(film, "_", " "),
      film = str_replace_all(film, "\\(.{1,}\\)", ""), #removes all things after ()
      film = str_replace_all(film, "( $)|(  )", "")
    )  
  
  return(raw_input)
}


list_urls_scraping <- map(oscar_links, get_wiki_urls) %>% do.call("rbind.data.frame", .) %>% distinct()

```

Unfortunately, a few movies were left "link-less" but I didn't have the time to go back and add them.

The above scraped **all** the urls found in the Academy Award pages linked below, so I merged this with the data I had collected on movies nominated from 2016 onward to determined which urls to scrape. Because I had scraped URLs indiscriminately, I ended up with a lot of redundant urls for every movie: for instance, `list_urls_scraping` has links to all four versions of A Star Is Born. I found the appropriate link by 1) making sure "film" was specified in the link (when multiple pages have the same basic URL, Wikipedia adds a descriptor like `(novel)` or `(film)` at the end) and 2) making sure the link was to the most recent version of the movie.

A few non-movie entries (Rachel Weisz?) were still included, so I removed them manually.

```{r Creating Dataset, optionwarning = FALSE, warning=FALSE }
#### CREATING DATASET ####
## Missing URLS 
left_join(nominees, list_urls_scraping) %>% filter(year >= 2016) %>% nrow()
left_join(nominees, list_urls_scraping) %>% filter(year >= 2016) %>% filter(is.na(link)) %>% nrow() # movies with missing links

## Narrowing URLs down to 2016 onward movies
infoless_movies <- left_join(nominees, list_urls_scraping) %>% 
  filter(year >= 2016) %>% 
  filter(!is.na(link)) %>%
  mutate(link = paste("https://en.wikipedia.org/", link, sep = "")) %>% 
  distinct(film, link)

## Sanity Check: Keeping right URL for each movie
extra_links <- infoless_movies %>% group_by(film) %>% count() %>% filter(n > 1)

correct_links <- infoless_movies %>% 
  filter(film %in% extra_links$film) %>%
  filter(str_detect(link, "film")) %>%
  mutate(year = str_extract(link, "\\(...._") %>% str_replace_all("\\(|_", "") %>% as.numeric()) %>%
  filter(is.na(year) | year >= 2016) %>%
  select(-year)

## Remove Extra URLS, Keep Correct Ones
infoless_movies <- infoless_movies %>% 
  filter(!(film %in% extra_links$film)) %>%
  rbind(., correct_links)

## Rachel Weisz is NOT a movie!!
infoless_movies <- filter(infoless_movies, !(film %in% c("Rachel Weisz", "Russell Bufalino", "Joe Pesci")))
```

I then had to use those links to retrieve the information I was interested in from the movie's page. Again, I turned one of the tables present on the page into a Dataframe using `html_table`, then subset the relevant rows.

```{r Movie-Specific Information, optionwarning = FALSE, warning=FALSE }
### GETTING MOVIE INFO FROM WIKIPEDIA ####
get_movie_info <- function(url){
  
  wiki_resp <- read_html(url)
  raw_input <- html_table(html_nodes(wiki_resp, ".infobox"), fill = TRUE)
  raw_input <- raw_input[[1]]
  raw_input <- as.data.frame(raw_input, stringsAsFactors = FALSE)
  names(raw_input) <- c("key_", "val_")
  
  ## Subsetting Relevant Rows
  col_nams <- c("Written by", "Starring", "Release date", "Running time", "Country", "Budget", "Box office")
  
  raw_input <- raw_input %>%
    filter(key_ %in% col_nams)
  
  ## Removing First Row, Using It As Column Names
  names_ <- unname(raw_input[ , 1])
  
  raw_input <- raw_input %>% t() %>% as.data.frame() 
  
  
  row.names(raw_input) <- c()
  names(raw_input) <- names_
  raw_input <- raw_input[2, ]
  
  ## Cleaning Output
  raw_input <- raw_input %>%
    mutate(
      link = url,
      writers_count = if_else(any(str_detect(names(raw_input), "Written by")), 1 , 0),
      stars_count = 1 + str_count(Starring, "\n"),
      running_time = str_replace_all(`Running time`, "\\[.{1,}\\]", ""),
      running_time = str_replace(running_time, "minutes", ""),
      release_date = str_extract_all(`Release date`, "....-..-.."), #extracting dates
      release_date = str_split(release_date, ",") %>% map(2) %>% str_replace_all("\\)", ""), #cleaning dates, picking second
      release_date = str_extract_all(release_date, "-..-") %>% str_replace_all("-", "") %>% as.numeric(), #cleaning date, picking month
      Country = str_split(Country, "\n") %>% map(1) %>% as.character()
    ) %>%
    mutate_if(is.factor, str_replace_all, "\\[.{1,}\\]", "") %>% #replace all content within brackets
    mutate_if(is.character, str_replace_all, "\\(|\\)", "") %>% #remove all ()
    select(- `Release date`, - Starring, - `Running time`)  
  
  ## Modifying writers_count as Needed
  if(any(str_detect(names(raw_input), "Written") == TRUE)){
    raw_input <- raw_input %>% mutate(writers_count = writers_count + str_count(`Written by`, "\n")) %>% select(- `Written by`)
  }
  
  ## Added NA when missing Info
  col_nams <- c("writers_count", "stars_count", "release_date", "running_time", "Country", "Budget", "Box office")
  
  for (i in col_nams){
    if (i %in% names(raw_input) == FALSE){
      raw_input[, i] <- NA
    }
  }
  
  return(raw_input)
}

oscars_new_info <- map(as.list(infoless_movies$link), get_movie_info) %>% do.call("rbind.data.frame", .)
```

### Merging Datasets

Finally, I was able to collect all the required information. The code below cleans the resulting dataset...

```{r Cleaning Datasets, optionwarning = FALSE, warning=FALSE }
## Adding Film Key
oscars_new_info <- oscars_new_info %>%
  mutate(film = infoless_movies$film) #the URLS are scraped in exact order they wered added in

## Missing Movie Information
mov1 <- nominees %>% 
  mutate(film = str_replace_all(film, "(^ )|( $)", "")) %>% 
  left_join(., oscars_new_info, by = "film") %>%
  filter(is.na(Country)) %>%
  distinct(film)
  #nrow()

## Cleaning Nominees, Adding New Information
nominees <- nominees %>% 
  mutate(film = str_replace_all(film, "(^ )|( $)", "")) %>% 
  left_join(., oscars_new_info, by = "film")

### Clean to Merge With OG Dataset
nominees_trim <- select(nominees, winner, award, category, year, country = Country, release_date, running_time, stars_count, writers_count)

## Splitting df to change pivot some columns
nominees_oscar <- nominees %>% filter(award == "oscar")
others <- nominees %>% filter(award != "oscar") %>% spread(award, winner, 0) #changes df so each award is a column, 0 used instead of NA
new_oscars <- left_join(nominees_oscar, others, by = c("year", "name", "film", "category", "Country", "Budget", "Box office", "link", "writers_count", "stars_count", "running_time", "release_date"))

new_oscars_trim <- select(new_oscars, winner, category, year, 
                          BAFTA, GG, Guild = Screen, country = Country, release_date, running_time, stars_count, writers_count)

```

Then adds the previous dataset ...

```{r Loading Previous Dataset ,optionwarning = FALSE, warning=FALSE }
### Loading Data ####
nominations <- read_csv("https://raw.githubusercontent.com/scruwys/and-the-award-goes-to/master/data/nominations.csv")  %>% 
  select(-href) 

films <- read_csv("https://raw.githubusercontent.com/scruwys/and-the-award-goes-to/master/data/films.csv")

### Cleaning Data ####
### Cleaning Strings
cleaning_money_strings <- function(vec_){
  if (is.na(vec_) == FALSE){
    vec_ <- substring(vec_, 2) #gets rid of first character ($)
    vec_ <- str_replace_all(vec_, ",", "") #gets rid of commas
    
    if (str_detect(vec_, "million") == TRUE){
      vec <- str_replace(vec_, "million.", "")
      vec_ <- as.numeric(vec_)
      vec_ <- vec_ * 1000000
    } else{
      vec_ <- as.numeric(vec_)
    }  
  }

  return(vec_)
}


films$bom_domestic <- map(films$bom_domestic, cleaning_money_strings) %>% unlist() %>% as.numeric()
films$bom_foreign <- map(films$bom_foreign, cleaning_money_strings) %>% unlist() %>% as.numeric()
films$bom_worldwide <- map(films$bom_worldwide, cleaning_money_strings) %>% unlist() %>% as.numeric()
films$budget <- map(films$budget, cleaning_money_strings) %>% unlist() %>% as.numeric()
films$box_office <- map(films$box_office, cleaning_money_strings) %>% unlist() %>% as.numeric()

### Splitting df to change pivot some columns
oscars <- nominations %>% filter(award == "Oscar")
others <- nominations %>% filter(award != "Oscar") %>%
  spread(award, winner, 0) #changes df so each award is a column, 0 used instead of NA
#could use -1 : penalty for not being nominated

### Merging Dataframes
oscars <- left_join(oscars, others, by = c("category", "film", "name", "year"))
names(oscars)[names(oscars) == 'Golden Globe'] <- "GG" #renaming golden globes
oscars <- left_join(oscars, films, by = c("film", "year"))
oscars <- mutate(oscars, release_date = month(as.Date(release_date, "%Y-%m-%d")))
```


... and finally merges the two together.

```{r Merging the Datasets, optionwarning = FALSE, warning=FALSE }
#trimming OG dataset  
oscars %>% names()
oscars_trim <- select(oscars, winner, category, year, BAFTA, GG, Guild, country, release_date, running_time, stars_count, writers_count)
oscars_trim %>% names()

head(oscars_trim)
head(new_oscars_trim)

tail(oscars_trim)
tail(new_oscars_trim)

oscars <- rbind(oscars_trim, new_oscars_trim)

## More Last Minute Cleaning
oscars <- oscars %>% 
  mutate(country = str_replace_all(country, "\\[.{1,}\\]", ""), #removing footnotes from country names
         running_time = as.numeric(running_time)) %>% 
  mutate_if(is.numeric, ~replace(., is.na(.), 0)) ##### 

# Removing Columns With Too Many Missing Values
cols_na <- apply(oscars, 2, is.na) %>% apply(., 2, sum)
oscars <- oscars[ , names(cols_na)[cols_na <= 395]]
oscars <- oscars[complete.cases(oscars), ]
```

### Prediction

The actual prediction steps are much shorter. I leverage `carat` and the `purrr` package to fit logistic and elastic net models on every category. After playing with the code for a little while, I found that the parsimonious model I was planning to use worked fairly well. Filtering the dataset to only keep more recent ceremonies also improved the accuracy of the model.

The logit model fares a little better than the elastic net, but both models' predictions are shown.

```{r Predictions, optionwarning = FALSE, warning=FALSE }
# Setting CV Parameter
set.seed(15)

ctrl <- trainControl(method = "cv", number = 10)

nnetGrid <- expand.grid(.decay = c(0, 0.01, 0.5, .1),    .size = c(1:30))

oscars$winner <- as.factor(oscars$winner)

## Comparing Models
### BINOMIAL
oscars %>% 
  filter(year >= 1995 & year < 2019) %>%
  split(.$category) %>%
  map(., select, winner, year, BAFTA, GG, Guild, release_date, running_time, stars_count, writers_count) %>%
  map(~ (train(winner ~ ., data = ., method = "glm", family = "binomial", trControl = ctrl))) %>%
  map("results") %>%
  map("Accuracy")

### Neural Net Model
#oscars %>% 
#  filter(year >= 1995 & year < 2019) %>%
#  split(.$category) %>%
#  map(., select, winner, year, BAFTA, GG, Guild, release_date, running_time, stars_count, writers_count) %>%
#  map(~ (train(winner ~ ., data = ., method = "nnet", tuneGrid = nnetGrid, preProcess = c("center", "scale"), trace = FALSE, trControl = ctrl))) %>%
#  map("results") %>%
#  map("Accuracy") %>%
#  map(mean)

### Using Models for Prediction
newdata <- oscars %>% filter(year == 2019)

log_models <- oscars %>% 
  filter(year >= 1995 & year < 2019) %>%
  filter(category != "Director") %>% #was unable to get new data for Directors
  split(.$category) %>% 
  map(., select, winner, year, BAFTA, GG, Guild, release_date, running_time, stars_count, writers_count) %>%
  map(~ (train(winner ~ ., data = ., method = "glm", family = "binomial", trControl = ctrl)))

map2(log_models, newdata %>% split(.$category), predict, type = "prob") %>% map("1")
nominees %>% filter(year == 2019 & award == "oscar") %>% split(.$category) %>% map(., select, name) %>% map("name")
```

